\bf Approximating Likelihood Ratios with Calibrated Discriminative Classifiers

### 2016-03-17 jasa/paper-jasa.tex
minor changes

    \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[clip, trim=0.5cm 0.5cm 0.5cm 0.5cm,width=\textwidth]{figures/fig1e.pdf}
        \caption{$p( \log \hat r(\hat{s}(\mathbf{x}))) \, | \,\gamma = 0.05)$ }
        \label{fig:decomposed_ratio}
    \end{subfigure}
    ~
    \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[clip, trim=0.5cm 0.5cm 0.5cm 0.5cm,width=\textwidth]{figures/fig1f.pdf}
        \caption{$-2\log \Lambda(\gamma)$ }
        \label{fig:likelihood}
    \end{subfigure}

    \caption{Example data $\mathcal{D}$ Various stages in Approximation of the log-likelihood ratio
             $\log r(\mathbf{x};\gamma=0.05,\gamma=0)$
             with calibrated classifiers. }
\end{figure}

@@

    \caption{Using approximated likelihood ratios for parameter inference yields an unbiased maximum likelihood estimator
            $\hat \gamma$, as empirically estimated 1000 times over re-sampled observed data.}
    \label{fig:2}
\end{figure}

>>>>

    \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[clip, trim=0.5cm 0.5cm 0.5cm 0.5cm,width=\textwidth]{figures/fig1e.pdf}
        \caption{$p( \log \hat r(\hat{s}(\mathbf{x})) \, | \,\gamma = 0.05)$ }
        \label{fig:decomposed_ratio}
    \end{subfigure}
    ~
    \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[clip, trim=0.5cm 0.5cm 0.5cm 0.5cm,width=\textwidth]{figures/fig1f.pdf}
        \caption{$-2\log \Lambda(\gamma)$ }
        \label{fig:likelihood}
    \end{subfigure}

    \caption{Histogram of $\mathcal{D}$ generated from $\gamma=0.05$ and plots illustrating various stages in 
    the approximation of the log-likelihood ratio  $\log r(\mathbf{x};\gamma=0.05,\gamma=0)$
             with calibrated classifiers (see text). }
\end{figure}

@@

    \caption{Using approximated likelihood ratios for parameter inference yields an unbiased maximum likelihood estimator
            $\hat \gamma$, as empirically estimated from an ensemble of 1000 artificial datasets.}
    \label{fig:2}
\end{figure}
